%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}

\usepackage[left=1.25in, right=1.25in, bottom=1.25in, top=1in]{geometry}



\pagenumbering{gobble} % not show page number

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}

\noindent  \LARGE{\textbf{IAMKAI}}  
\normalsize
\end{center}

	\section*{Skill}
	\nointerlineskip
	\noindent\rule{450pt}{0.4pt}
	
	\begin{itemize}
	\item Familar with version control system(git) and CI tool(Travis CI).
  	\item Imporve multi-mode resource-constrained project scheduling 10 percent performace using Apache spark.
  	\item Experienced in performance analysis and debugging tool such as perf, gdb.
  	\item Develope automatic tools for some repeative tasks using shell and python script.
	\end{itemize}


	
	\section*{Education}
	\nointerlineskip
	\noindent\rule{450pt}{0.4pt}
	  \begin{itemize}
	  \item 2017/09 - 2019/06
	  \vspace{-5pt}
	  \item[] Master in Department of Computer Science and Information Engineering,
      \\ National Cheng Kung University of Electrical Engineering and Computer Science.
	  \end{itemize}
	  
	  
	  \begin{itemize}
	  	\item 2013/09 - 2017/06 (expected)
	  	\vspace{-5pt}
	  	\item[]       Department of Computer and Communication Engineering, 
      \\National Kaohsiung First University of Science and Technology
	  \end{itemize}


	\section*{Experience}
	\nointerlineskip
	\noindent\rule{450pt}{0.4pt}
	
	\begin{itemize}
		\item Earned Honorable Mention in the ITSA XX Contest
		\item Participate in The 20XX ITSA Annual Collegiate Programming Contest
		
	\end{itemize}
		

	\section*{Projects}
	\nointerlineskip
	\noindent\rule{450pt}{0.4pt}
	\begin{itemize}
	\item Undergraduate Research: Compare the performace  between the spark and hadoop for multi-mode resource-constrained project scheduling.
	\item Write SELinux policy to enhance the security level on OS for NCSIST.
	\item Port Mopidy music player on respberry pi, and customize the software music equalizer on webpage.
	\item Apply SIMD instruction to improve phonebook performance.
	\end{itemize}

	
\end{document}
